Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-09 paper.tex
Revising abstract
Please @amoragar have a look.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
***TO DO***: rewrite this considering the new contents and results\\

When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
Several years 
% % Antonio - Decir cuántos años son, que no me acuerdo.
% of data on published books in Spain have been processed by means of
% data visualisation %visualization does not "process". I propose an alternative
%  and other feature selection techniques. 
We have been working on a data set that includes the complete sales
data for books published in Spain across several years. After an
initial exploratory phase using visualisation techniques, we have
applied several feature selection techniques in order
to find out what are the variables that have more impact on sales, and
then used machine learning to create a model and forecast sales. 
The described methodology improves the forecasting running time  %with
                                %respect to what?- JJ
and is
eventually able to predict sales with remarkable accuracy. Moreover,
the proposed method was validated by the company that provided
the data and incorporated in a business intelligence tool for
publishers, % We shouldn't say this, it's outside the bounds of the
            % paper. Besides, it was a different technique - JJ
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%***TO DO***: rewrite this considering the new contents and results\\

When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
% % Antonio - Decir cuántos años son, que no me acuerdo.
% of data on published books in Spain have been processed by means of
% data visualisation %visualization does not "process". I propose an alternative
%  and other feature selection techniques. 
We have been working on a data set that includes the complete sales
data for books published in Spain across several years. After an
initial exploratory analysis phase using visualisation techniques, we have
applied several feature selection techniques in order
to find out what are the variables that have more impact on sales, and
then used machine learning to create a model and forecast sales. The
initial methodology was used in a commercial product by Grupo
Trevenque, but the methodology described here improves the forecasting running time  %with
                                %respect to what?- JJ
and is
eventually able to predict sales from pre-publication data with
remarkable accuracy, thus creating a useful tool for publishers, for whom
% Moreover,
% the proposed method was validated by the company that provided
% the data and incorporated in a business intelligence tool for
% publishers, % We shouldn't say this, it's outside the bounds of the
            % paper. Besides, it was a different technique - JJ
obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation. 
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}
